Are We Reusing Outdated Code from Stack Overflow?

### 2016-11-10 latex-acm/cloneoverflow.tex

In this study, we treat code snippets that are copied from software systems to Stack Overflow, and vice versa, as code clones. We call them \textbf{online code clones}. There are three ways to create online code clones: 1) code is cloned from a software project to Stack Overflow as an example; 2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; and 3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium. Online code clones can similarly lead to a problem of bug propagation as classical code clones. Unfortunately, they are more difficult to locate and fix since the search space from online corpora is larger and no longer confined in a local repository.

@@

\textbf{Open source systems}: we selected an established corpus for empirical software engineering studies called \textbf{Qualitas} \cite{QualitasCorpus}. \FIXME{more details about Qualitas and why we chose it}. We selected the 20130901r version of Qualitas corpus containing 112 Java open source projects with releases no later than 1st September 2013. We chose the snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old which is sufficient for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there are 3 projects, \textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}, that do not contain any Java source code file so they are removed from the study. This results in totally 109 projects analysed in the study. As shown in \Cref{tab:datasets}, the 109 Qualitas project have 138,238 Java files containing 16,081,899 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

\subsubsection{Clone Detectors}
There are a number of restrictions in terms of choosing clone detection tools for this study. Firstly, they have to compatible with Java. Secondly, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets which are not in a complete block or not compilable. Thirdly, since the amount of code that have to be processed are in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time. We have tried running 5 state-of-the-arts clone detectors including Simian \cite{simian}, NiCad \cite{Cordy,Roy2008}, CCFinder \cite{Kamiya2002}, iClones \cite{Gode2009}, and DECKARD \cite{Jiang2007a} against the Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD failed to successfully detect clones between 144,075 Stack Overflow code snippets and 109 Qualitas projects. All of them reported execution errors after running for couple of hours. Thus, we removed them from the study. Simian and NiCad completed the detection with success. We found that both of them are flexible enough to handle million-SLOC code corpus with method or class incompleteness. So, we decided to use both of them.

\textbf{Simian} is a text-based clone detector which locate clones at line-level granularity and has been used extensively in several clone studies \cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}. It is a command-line tool which enables us to automate the detection. It also offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect clones of type 1 and type 2. \textbf{NiCad} is also a text-based clone detector which detects clones at either method- or block-level granularity. It can detect clone up to type 3 and is used in several clone studies \cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}. It utilises TXL for parsing and pretty-printing source code. It also provide code normalisation by variable renaming and code abstraction. We use a variant of NiCad called \textit{nicadcross}. It offers the same functionalities as the original NiCad but is specialised for detecting code clones between two systems. NiCad is also a command-line tool which makes it suitable for automation.

\subsubsection{Agreement-based Clone Detection}
The number of detected clones between the two datasets can be very large and infeasible for human to manually check all of them. Therefore, we adopted an idea of clone agreement which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}. By using this agreement-based clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the agreed clone pairs. To find agreement of two clone pairs, we resort to an approach proposed by a study by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have overlapping clone lines can be considered as a good-match or an ok-match pair. A good-match clone pair has stronger agreement than an ok-match pair. We follow the same following definitions introduced in the original paper:

%good and ok-match clone pairs are defined as follows. 
A clone pair \textit{CP} is formed by two clone fragments \textit{CF$_1$} and \textit{CF$_2$} with a pre-defined similarity threshold \textit{t}: \textit{CP} = (\textit{CF$_1$}, \textit{CF$_2$}, \textit{t}).  We can define \textit{overlap} and \textit{contained} value of two clone pairs as 
%\squeezeup
\begin{multline}
	overlap(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|} 
\end{multline}
%\squeezeup
\begin{multline}
	contained(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}. 
\end{multline}

@@

Furthermore, \textit{ok-value} is defined as
%\squeezeup
\begin{align*}
	ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) = min(max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1)),
	\\ max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2), \\contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2))).
\end{align*}

@@

Using this good-match and ok-match criteria with a predefined threshold \textit{p}, we prune the detected clone pairs for manual investigation. good-match pairs are the ones with the highest confident to be true clones, followed by ok-match pairs, and followed by clone pairs without agreement.

\subsection{Clone detectors' parameter tuning}
We are aware of effects of configurations to clone detection results and needs for searching for optimised configurations in empirical clone studies \cite{Wang2013,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the size of the two datasets and search space of at least 15 of Simian's and 5 of NiCad's parameters, we are hindered from finding the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established settings: 1) the tools' default settings chosen by the tools' creators (denoted as \textit{df}), and 2) the general settings for Java sets from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}). The details of the two configurations are described in \Cref{t:param_tuning}. With our two tools and these two sets of configurations, we look for agreements in four possible pair-wise combinations: Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$.

@@

The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} settings are presented in \Cref{tab:raw_stats}. Preliminary manual investigation of Simian's clone report showed that there were problematic 11 fragments. These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones of array initialisation. Hence, they were removed from Simian's clone reports before the analysis. From \Cref{tab:raw_stats}, Simian clones are from approximately 10\% of the 144,075 Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively. NiCad$_{df}$ reports clones from 1,197 Stack Overflow code snippets while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones from a large amount of 12,884 snippets due to its relaxed settings. In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report a large number of clone pairs of 59,936,722 and 206,718,663 respectively. This is expected since EvaClone configurations prefer recall \cite{Wang2013}. The average clone size of Simian$_{df}$ is 7.45 which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.81. Similarly, NiCad$_{df}$ has an average clone size of 9.54 which is bigger than 5.31 reported by NiCad$_{\textrm{\textit{EvCl}}}$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones but result in higher agreements. The average percentage of code in Stack Overflow snippets that are clones reported by Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 28\%, 29\%, 25\% and 21\% accordingly.

@@

\subsection{Agreement based clone pairs}

We use a threshold \textit{p} of 0.7 for both good and ok-match. A visualisation of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} settings can be seen from \Cref{fig:venn4_orig_good}. We found that NiCad throws renaming and clustering errors while processing some Qualitas projects as listed in \Cref{tab:projects_missing}. %This resulted in not all 109 projects had NiCad clone reports. 
NiCad$_{\textrm{\textit{df}}}$, produced clustering errors for 6 projects. NiCad$_{\textrm{\textit{EvCl}}}$ produced renaming error for 4 projects, and clustering error for 13 projects. As a result, we did not have NiCad clone reports for these projects and hence they are missing from agreement-based clone pair calculation. \FIXME{Report the errors to NiCad creator.} There are 2,261 unique good-match pairs consisting of 10 pairs from Simian$_{df}$-NiCad$_{df}$, 26 pairs from Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$. \Cref{fig:venn4_orig_ok} show the distribution of 23,868 unique ok-match pairs, which subsume the good-match pairs. There are 3,800 pairs from Simian$_{df}$-NiCad$_{df}$, 1,017 pairs from Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, 88 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and 19,777 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$. Between the four sets, there are a few clone pairs that are common between two adjacent sets, but there is no clone pair that is agreed by all four combinations.

@@

@@

The classification scheme is described in \Cref{tab:classification_scheme} and the classification results are shown in \Cref{tab:classification_good_o}. We have manually investigated all of the 2,261 good-match clone pairs.  However, for the ok-match clone pairs, we could not feasibly investigate 23,868 pairs manually.  According to the manual investigation of good-match results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number of 2,225 false positive results (accounts for 99.87\% of Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ clone pairs). We thus decided to leave them out of the manual investigation. There are totally 4,625 ok-match pairs that were investigated. The 49 true positive pairs found are combinations of 12 unique Stack Overflow fragments, and 14 unique Qualitas Java files from 10 different projects.

Since we are not certain about the direction of copying in the B-classified pairs, we checked the modification time of each Java file in Qualitas project and compare it to the timestamp of Stack Overflow answers. We found that all Stack Overflow code fragments were posted after their respectively similar Java files in Qualitas project. This means that the copying can only be either (1) from Qualitas to Stack Overflow or (2) from a third source to both Stack Overflow and Qualitas independently.

%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvCl}}}$-NiCad$_{\mathrm{\textit{EvCl}}}$ altogether due to its large number of false positive. With the remaining 3 agreements, we did manual investigation of agreed ok-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{EvCl}}}$, and Simian$_{\mathrm{\textit{EvCl}}}$-NiCad$_{df}$. We had not done any investigation of good-match since there were no good-match pairs for these 3 agreements. The number of pairs that have been looked at is 6,706 (excluding duplicates). The results are shown in Table.

\begin{table*}
	\centering
	\caption{Classification results of agreement-based and non agreement-based clone pairs)}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\hline
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 33  & 8 & \textbf{49} & 12 & 14 & 10 & 4459 & 35 & 82 & \textbf{4576} & 99 & 136 & 29 & \textbf{4625} & 110 & 150 & 33 \\
		\hline 
		\hline 
		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 36 & 0 & 229 & 3 & \textbf{268} & 76 & 151 & 14 & 169 & 52 & 14 & \textbf{235} & 92 & 119 & 22 & \textbf{503} & 164 & 261 & 24 \\
		\multirow{1}{*}{\textit{Simian$_{df}$}} & 71 & 0 & 318 & 11 & \textbf{401} & 138 & 210 & 37 & 182 & 64 & 148 & \textbf{394} & 120 & 191 & 45 & \textbf{795} & 246 & 386 & 55 \\
		\hline
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 10 & 0 & \textbf{10} & 7 & 8 & 5 & 6 & 3 & 26 & \textbf{35} & 17 & 16 & 8 & \textbf{45} & 24 & 24 & 9 \\ 
		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 15 & 0 & \textbf{19} & 15 & 13 & 9 & 30 & 6 & 104 & \textbf{140} & 51 & 55 & 20 & \textbf{159} & 66 & 68 & 23 \\ 
		\hline
		%		\multirow{1}{*}{\textit{NiCad$_{df}$}*} & 4  & 0 & 1 & 0 & \textbf{5} & 4 & 5 & 3 & 23 & 1 & 67 & \textbf{91} & 28 & 31 & 10 & \textbf{96} & 33 & 37 & 13 \\ 
			%		\hline
	\end{tabular} 
	}
\end{table*}

>>>>

In this study, we treat code snippets that are copied from software systems to Stack Overflow, and vice versa, as code clones. We call them \textbf{online code clones}. There are three ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; and (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium. Online code clones can similarly lead to a problem of bug propagation as classical code clones. Unfortunately, they are more difficult to locate and fix since the search space from online corpora is larger and no longer confined in a local repository.

@@

\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas} \cite{QualitasCorpus}. It is a curated Java corpus that has been used in several software engineering studies \cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation \cite{QualitasCorpus}. We selected the 20130901r snapshot of Qualitas corpus containing 112 Java open source projects. This release contains projects with releases no later than 1st September 2013. We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment, January--December 2016. The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there are 3 projects; \textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}; that do not contain Java source code so they are removed from the study. This results in totally 109 projects analysed in the study. As shown in \Cref{tab:datasets}, the 109 Qualitas project have 138,238 Java files containing 16,081,899 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

\subsubsection{Clone Detectors}
There is a number of restrictions in terms of choosing clone detection tools for this study. Firstly, they have to support Java. Secondly, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable. Thirdly, since the amount of code that have to be processed are in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time. We have tried running 5 state-of-the-art clone detectors including Simian \cite{simian}, NiCad \cite{Cordy,Roy2008}, CCFinder \cite{Kamiya2002}, iClones \cite{Gode2009}, and DECKARD \cite{Jiang2007a} against Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD failed to successfully detect clones between 144,075 Stack Overflow code snippets and 109 Qualitas projects. All of them reported execution errors after running for couple of hours. Thus, we removed them from the study. Simian and NiCad completed the detection with success. We found that both of them are also flexible enough to handle million-SLOC code corpus with method or class incompleteness. So, we decided to use both of them.

\textbf{Simian} is a text-based clone detector which locate clones at line-level granularity and has been used extensively in several clone studies \cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}. It is a command-line tool which enables us to automate the detection. Furthermore, it offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect clones of type 1 and type 2. \textbf{NiCad} is also a text-based clone detector which detects clones at either method- or block-level granularity. It can detect clones up to type 3 and is used in several clone studies \cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}. It utilises TXL for parsing and pretty-printing source code. It also provide code normalisation by variable renaming and code abstraction. We use a variant of NiCad called \textit{nicadcross}. It offers the same functionalities as the original NiCad but is specialised for detecting code clones between two systems. NiCad is also a command-line tool which makes it suitable for automation.

\subsubsection{Agreement-based Clone Filtering}
The number of detected clones between two datasets  can be very large. In our study, there are totally 266,837,480 clone pairs reported. It is infeasible for human to manually validate all of them. One can do sampling of clones from this huge clone pair set. However, they may end up having most of them false positive clones. Therefore, we adopted an idea of clone agreement which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish. Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}. By using this agreement-based clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools. To find agreement of two clone pairs, we resort to an approach proposed in a study by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair. A good-match clone pair has stronger agreement than an ok-match pair. We follow the same following definitions introduced in the original paper.

%good and ok-match clone pairs are defined as follows. 
A clone pair \textit{CP} is formed by two clone fragments \textit{CF$_1$} and \textit{CF$_2$} with a pre-defined similarity threshold \textit{t}, i.e. \textit{CP} = (\textit{CF$_1$}, \textit{CF$_2$}, \textit{t}).  We can define \textit{overlap} and \textit{contained} value of two clone pairs as 
%\squeezeup
\begin{multline}
	overlap(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|} 
\end{multline}
%\squeezeup
\begin{multline}
	contained(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}. 
\end{multline}

@@

\textit{ok-value} is defined as
%\squeezeup
\begin{align*}
	ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) = min(max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1)),
	\\ max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2), \\contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2))).
\end{align*}

@@

Using this good-match and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266-million candidate clone pairs for manual investigation. good-match pairs are the ones with the highest confident and ranked the first to be looked at, followed by ok-match pairs, and followed by clone pairs without agreement.

\subsection{Clone detectors' parameter tuning}
We are aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2013,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}. However, considering the size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we are hindered from searching for the best configurations of the tools. Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{df}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}). The details of the two configurations are described in \Cref{t:param_tuning}. Having two clone detectors multiplied by two chosen configurations, we look for agreements in four possible pair-wise combinations: Simian$_{df}$--NiCad$_{df}$, Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.

@@

The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} configurations are presented in \Cref{tab:raw_stats}. Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments. These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones of array initialisation. Hence, they were removed from Simian's clone reports before the analysis. From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively. NiCad$_{df}$ reports clones in 1,197 Stack Overflow code snippets, while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones in a larger number of 12,884 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report an enormous number of clone pairs of 59,936,722 and 206,718,663 respectively. This is expected since EvaClone configurations prefer recall \cite{Wang2013}. The average clone size of Simian$_{df}$ is 7.45 lines which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.81. Similarly, NiCad$_{df}$ has an average clone size of 9.54 lines which is bigger than 5.31 reported by NiCad$_{\textrm{\textit{EvCl}}}$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones. The average percentage of Stack Overflow code snippets that are cloned according to Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 28\%, 29\%, 25\%, and 21\% accordingly.

@@

\subsection{Agreement-based clone pairs}

Agreement-based clone pairs are clone pairs that pass Bellon's criteria and selected for manual investigation. We select a threshold \textit{p} of 0.7 for both good and ok-match similar to the original study \cite{Bellon2007}. The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. NiCad generated errors and stopped processing while it was analysing some Qualitas projects. \FIXME{Report the errors to NiCad creator.}  NiCad$_{\textrm{\textit{df}}}$ unsuccessfully detected clones in 6 projects due to clustering errors. For NiCad$_{\textrm{\textit{EvCl}}}$, the tool generated renaming errors for 4 projects, and clustering errors for 13 projects. As a result, we did not have NiCad clone candidates for 6 (\textit{df}) and 27 projects (\textit{EvCl}) in the agreement-based clone pairs. Unfortunately, this also has an effect to Simian clone candidates of the same projects to be removed from the agreement-based clone pairs since they do not have matching clone pairs. The distributions of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} configurations are depicted in \Cref{fig:venn4_orig_good}. There are 2,261 unique good-match pairs consisting of 10 pairs from Simian$_{df}$--NiCad$_{df}$, 26 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$. ok-match clone pairs subsume the good-match pairs according to the criteria. As a result, there are 23,868 clone pairs, which are 3,800 pairs from Simian$_{df}$--NiCad$_{df}$, 1,017 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 88 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 19,777 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$. Between the four configuration sets, there are a few clone pairs that are shared between two adjacent sets, but there is no clone pair that is agreed by all four combinations.

@@

\subsubsection{Classifications of online code clones}

We need an appropriate classification scheme to be able to meaningfully manually categorise the selected clone candidates. We adapted the classifications from a study by Kapser et al. \cite{Kapser2006}. The online code clone classification scheme is described in \Cref{tab:classification_scheme}. Due to differences in the experimental settings of the study, we adopted some of the original classifications and added a few more classifications to match with our datasets and context. The final seven categories (A--F) have been observed to be common clone patterns found from a manual check of 100 random sample clone pairs. Category A is a clone pair that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation or links in Stack Overflow post), and vice versa in category A'. Category B is a clone pair that is exactly identical or highly similar but without any attribution of copying. Category C is a clone pair that has information confirming of copying but from the same external source. Category D is a clone pair that is either boiler-plate code (e.g. \verb|equals()| methods, or getters and setters) or IDE-generated (e.g. GUI initialisation). Category E are clones created by inheriting the same super class or implementing the same interface. They usually share similar overriding methods. The last category, category F, are false clones that have accidental similarity after code normalisation or other causes. Using this classification scheme, we consider clone pairs in category A, A', B, C as true positive, and clone pairs in category D, E, F as false positive.

@@

The first author who has been working on clone detection research for two years takes the role of an investigator who performs manual investigation. Following the classification scheme, the investigator manually goes through each agreement-based clone pair, looks at the clones, and chooses the most appropriate category for the pair. A relevant and useful observation is also recorded for each clone pair. The classification results are shown in \Cref{tab:classification_good_o}. We have manually investigated 2,261 good-match clone pairs. There is one clone pair found to be copied from a Qualitas project to Stack Overflow, 4 pairs that are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code), and 3 pairs that are copied from external sources. The rest are false positive clones. 58 clone pairs are found to \verb|equals()| methods, or getters and setters. Six pairs are similar code from inheritance of the same superclass or implementing the same interface. Finally, 2,189 clone pairs are false clones.

For the ok-match clone pairs, we could not feasibly investigate 23,868 pairs manually.  According to the manual investigation of good-match results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number of 2,253 false positive results (accounts for 99.87\% of Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ clone pairs) due to its recall preference. We thus decided to leave this configuration out of the ok-match manual investigation. There are totally 4,625 ok-match pairs that were investigated. The 49 true positive pairs found are combinations of 8, 33, and 8 clone pairs in category A, B, and C respectively.

We cannot be certain about the direction of copying in the category-B pairs, since there is no solid information of copying. We thus checked the timestamp of each Java file in Qualitas project and compared it to their respective timestamp of Stack Overflow posts. We found that all Stack Overflow posts were created after their respectively Qualitas Java files \FIXME{check again since the dataset is updated}. This means that the copying can only be either (1) from Qualitas to Stack Overflow or (2) from an external source to both Stack Overflow and Qualitas independently. There is no clone pairs found in A' category.

%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvCl}}}$--NiCad$_{\mathrm{\textit{EvCl}}}$ altogether due to its large number of false positive. With the remaining 3 agreements, we did manual investigation of agreed ok-match clone pairs from agreements of Simian$_{df}$--NiCad$_{df}$, Simian$_{df}$--NiCad$_{\mathrm{\textit{EvCl}}}$, and Simian$_{\mathrm{\textit{EvCl}}}$--NiCad$_{df}$. We had not done any investigation of good-match since there were no good-match pairs for these 3 agreements. The number of pairs that have been looked at is 6,706 (excluding duplicates). The results are shown in Table.
